### 2013-09-09 thesis/src/chapters/chapter-4.tex
Add view on a hybrid cloud

\subsubsection*{View on hybrid cloud}

>>>>

\subsubsection*{View on hybrid cloud}
When it comes to the application of a hybrid model in industry, in most cases the definition introduced in the previous chapter now becomes a 'public-private' composition. And this is how the term should be understood when discussing the results of the surveys which aimed to provide insights onto the view on a hybrid cloud from the customers' perspective.
The study \cite{NBSurvey13} forecasts 16 percentage growth in the hybrid cloud adoption in 5 years, from 27 to 43 percent. At the same time, the usage of a public model will decline from 39 to 32 percent.
The other survey, conducted by Rackspace \cite{RackspaceSurvey13}, provides more detailed data about current usage and popularity of a hybrid model. The first interesting finding is that as much as 60\% responders, which included 1300 companies in the UK and US, have moved or are planning to move certain applications either partially (41\%) or completely (19\%) off the public cloud because of its limitations or the potential benefits of other models, e.g. the hybrid one. The second one is about the pros of adopting the hybrid cloud  -- potential users find more control (59\%) and better security (54\%) top benefits of using this deployment model. The other most responded benefits are shown in the figure \ref{ch4:hybrid-cloud-top-benefits}.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-4/hybrid-cloud-top-benefits}
  \end{center}
  \caption{Top benefits of using the hybrid model according to \cite{RackspaceSurvey13}}
  \label{ch4:hybrid-cloud-top-benefits}
\end{figure}
